\section{Introduction}

\subsection{Purpose}%\subsection{Background}
This document describes the software requirements and specifications for the SMSEncryption mobile application.
\vspace{10pt}\\
The document will be used to ensure requirements are well understood by all stakeholders. It is therefore intended for all stakeholders of the project; including the developers and customers.


\subsection{Background}
Reliable communication using newer generation cellular technologies, such as GSM or 3G, is not always possible in certain parts of South Africa, as the signal for these technologies are either non-existent, or intermittent.
\vspace{10pt}\\
Therefore, communication normally occurs using SMS technology, which is generally not very secure. Messages sent via SMS are generally encrypted with a weak and broken stream cipher, and can thus be read by any competent attacker who intercepts the SMS. SMS messages are also stored on an SMSC for up to 15 days, which can then be viewed by an unknown party. This can cause a loss in confidentiality, integrity and availability of the communicators.
\vspace{10pt}\\
There is a need to develop a secure way of communicating using conventional mediums such as SMSes.

\subsection{Scope}
%objectives, goals, benefits, 
%Relate the software to corporate goals or business strategies.
The goal of this project is to create a mobile application which can be used to encrypt text before sending it via SMS technology, which can be decrypted on the receiving end. The application must be able to be used on more than one platform (i.e. iOS and Android).
\vspace{10pt}\\
By using the SMSEncryption application, the user will be able to encrypt messages which can only be decrypted by using the same application on the receiving end. The application will require local authentication in order to gain access to the appliaction and make use of it's features.
\vspace{10pt}\\
The benefit of this application is that you can use SMS technology to send confidential messages which can only be viewed by you and the desired recipient of the message - who is the only party who can unencrypt the message.

%Perhapts put this section below, higher up in the document, as some of these abbreviations are already used in the text above?
\subsection{Definitions, acronyms and abbreviations}
\begin{itemize}
\item SMSEncryption - The name of the current project which will allow users to encrypt and decrypt text with the main purpose of it being sent as an SMS, or via other messaging applications such as WhatsApp, WeChat, Facebook chat etc.
\item Message - The text intended to be sent from a sender to a receiver  or stored once said message has been encrypted via SMSEncryption.
\item Plaintext -  Is information a sender wishes to transmit to a receiver. 
\item Ciphertext - Is the result of encryption performed on plaintext using an algorithm, called a cipher.
\item Encrypt -  To alter the plaintext using an algorithm so as to be unintelligible to unauthorized parties.
\item Decrypt - The act of decoding a ciphertext back into the orginal form before conversion took place.
\item User - An authorised person who will interact with the application.
\item Sender - The person who authored and intends to send a messagethat has been encrypted via the application.
\item Receiver - The intended party who receives a message which has been encrypted via the application.
\item SMS - Short Message Service (SMS) is a text messaging service component of phone, Web, or mobile communication systems. This allows for short messages to be sent to other devices over a network which is not controlled by the sender or receiver.
\item SMSC - Short Message Service Centre (SMSC) is a network element in the mobile telephone network. Its purpose is to store, forward, convert and deliver SMS messages.
\item GSM - Global System for Mobile Communications (GSM) is a second generation standard for protocols used on mobile devices.
\item Entropy -  The expected value of the information contained in a message.
\end{itemize}

\subsection{Document Conventions}
\begin{itemize}
\item Documentation formulation: LaTeX
\item Naming convention: Crows Foot Notation
\end{itemize}

\subsection{References}
\begin{itemize}
\item{Kyle Riley - MWR Info Security}
\begin{itemize}
\item face-to-face meeting
\item email
\end{itemize}

\item{Bernard Wagner - MWR Info Security}
\begin{itemize}
\item face-to-face meeting
\item email
\end{itemize}
%\item{websites???}
\end{itemize}

\subsection{Overview}
%Structure of the rest of the SRS, in particular:
%organization for Section 3 (Specific Requirements)
%deviations from the standard SRS format
The rest of the document will be organized to include the following sections: General Description and Specific Requirements for the SMSEncryption application.
\vspace{10pt}\\
The General Description section will provide a background to the reader for the SMSEncryption application, and contains the following sections: Product Perspective, Product Functions, User Characteristics, Constraints and Assumptions and Dependencies.
\vspace{10pt}\\
The Specific Requirements section contains requirements for the SMSEncryption application, and is organised by application features. This is done in such a way that it will highlight the functions of the application. 
\vspace{10pt}\\
The sections contained in Specific Requirements include External Interface Requirements, System Features, Performance Requirements, Design Constraints, Software System Attributes, and Other Requirements.
\vspace{10pt}
%Appendices consist also of minutes of customer interviews
%and meetings, and do not constitute additional
%requirements of the software; i.e., all requirements arising
%from these minutes have been incorporated into the
%specific requirements in Section 3


