\subsection{Performance Requirements}
\begin{itemize}
\item The application should operate in a timely manner, the user should not be made to wait an unreasonable amount of time (this variable can be affected by the system environment e.g. resource availability).
\item The encryption method must be secure.
\end{itemize}



\subsection{Design constraints}
\subsubsection{Message length : DC1}
\textbf{(Source: Bernard Wagner, Priority: High)}
\begin{itemize}
\item Due to the fact that the primary messaging service which the client intends to use is SMS this limits the input size of the text to 160 characters. To maintain consistency we enforce this as the maximum length of messages which the application can encrypt and decrypt.
\end{itemize}
\subsubsection{The usable characters : DC2}
\textbf{(Source: Bernard Wagner, Priority: High)}
\begin{itemize}
\item The usable character which can be encrypted by the application is the GSM character set because the primary intended messaging service that the client wishes to use is SMS. 
\end{itemize}
\subsubsection{Application resource requirementsr : DC3}
\textbf{(Source: Bernard Wagner, Priority: High)}
\begin{itemize}
\item The application should function efficiently with the least amount of resource usage.
\end{itemize}


\subsection{Software system attributes}
\subsubsection{Reliability}
\begin{itemize}
\item The application should run until the user closes it.
\item Any information stored in the application should be static and exist as long as the application is open or said information is removed/edited.
\item The Cypher text should decrypt into its plaintext.
\end{itemize}
\subsubsection{Availability}
\begin{itemize}
\item The user should be able to use the application as long as it is running and should not be made to wait while the application performs a function.
\item The application should not interfere with any other applications which are running on the device.
\end{itemize}
\subsubsection{Security}
\begin{itemize}
\item A secure encryption and decryption method with entropy of no more than one percent will have to be used.
\end{itemize}
\subsubsection{Maintainability}
\begin{itemize}
\item The source code should be maintainable (simplistic and readable/documented).
\item The application should not act in unpredictable ways.
\end{itemize}
\subsubsection{Portability}
\begin{itemize}
\item The client has requested that different versions of the application be developed to execute on different operating systems namely Android and IOS.
\end{itemize}